# Reading List

```{r echo=FALSE}
library(RefManageR)
BibOptions(style = "markdown", bib.style = "authoryear", first.inits = FALSE,
           no.print.fields = c("issn", "isbn",
                               "eprint", "eprinttype",
                               "url", "urldate",
                               "series"),
           check.entries = FALSE)
```

## Structure, culture, and the (re)production of community {#scr}

\setlength\parindent{-1cm}
\setlength\leftskip{1cm}

```{r echo=FALSE, results='asis', warning=FALSE}
scr <- ReadBib("bib/01-structure-culture-reproduction.bib")
scr
```

\setlength\parindent{0cm}
\setlength\leftskip{0cm}

## Practices of inclusion and exclusion {#pie}

\setlength\parindent{-1cm}
\setlength\leftskip{1cm}

```{r echo=FALSE, results='asis', warning=FALSE}
pie <- ReadBib("bib/02-practices-inclusion-exclusion.bib")
pie
```

\setlength\parindent{0cm}
\setlength\leftskip{0cm}

## Changes and consequences {#cc}

\setlength\parindent{-1cm}
\setlength\leftskip{1cm}

```{r echo=FALSE, results='asis', warning=FALSE}
cc <- ReadBib("bib/03-changes-consequences.bib")
cc
```

\setlength\parindent{0cm}
\setlength\leftskip{0cm}
